Last glacial cycle glacier erosion potential in the Alps

### 2020-12-15 articles/erosion/alps-erosion.tex
Update erosion paper authors and figure outline.

\title{Last glacial cycle glacier erosion potential in the Alps}

\author[1]{Julien Seguinot}
\author[2]{Susan Ivy-Ochs}

\affil[1]{Laboratory of Hydraulics, Hydrology and Glaciology,
          ETH Zürich, Switzerland}
\affil[2]{Laboratory of Ion Beam Physics, ETH Zürich, Switzerland}

@@

    Fig.~\ref{fig:photos} -- Alpine glacial erosion landscape photos.
        (a) piedmont overdeepening (ca. 100 km), Lake Geneva
        (b) glacial valley (ca. 10 km), Lauterbrunnen
        (c) mountain cirque (ca. 1 km), Chüebodengletscher

@@

    Fig.~\ref{fig:evolution} -- Erosion rate snapshots or scatter plots.

>>>>

\title{Last glacial cycle glacier erosion potential in the Alps}
\author{Julien Seguinot}
\affil{Anafi, Greece}

@@

    Fig.~\ref{fig:landscape} -- Alpine glacial erosion landscape photos.
        (a) piedmont overdeepening (ca. 100 km), Lake Geneva
        (b) glacial valley (ca. 10 km), Lauterbrunnen
        (c) mountain cirque (ca. 1 km), Chüebodengletscher

@@

    Fig.~\ref{fig:transects} -- Erosion rate along transects.
    Fig.~\ref{fig:evolution} -- Erosion rate and ice volume.
    Fig.~\ref{fig:hypsogram} -- Erosion rate and elevation.
